---
title: "BA-BINTV2006U  Programming and Data Analysis for Business: Exercise 1"
author: "by Felix Thomsen, Alexander Schiøtz, Anders Laurents, Bertram Hage"
date: "2024-10-01"
output: 
  html_document:
    theme: sandstone
    code_folding: show
---

## 1. Data
<!-- 1. Write a short section about your data and why it is interesting to work with this data. -->

The dataset we have chosen contains a good amount of variables that can be analyzed to understand which factors affects student performance. The dataset contains information about hours studied, exam scores, and other variables that offers insights into which variables have the most impact on student performance. Working with this dataset allows us to identify key predictors for a student's performance and can be used for schools to understand how to improve academic success.

## 2. Data structure
<!-- 2. Load the dataset into R and inspect its structure. How many rows, how many columns, what is the
summary statistics for the numeric variables? -->
```{r init, warning = FALSE, message=FALSE}
library(knitr)
library(markdown)
library(rmarkdown)
library(tidyverse)
library(lubridate)
library(readxl)
theme_set(theme_bw())
```
```{r}
# Add code here
# Import csv
data <- read_csv("data.csv")
```

The dataset consists of **6,607 rows** and **20 columns**. 

#### Summary statistics for the numeric variables:
- **Hours Studied**: The number of hours studied by students ranges from 1 to 44 hours, with a median of 20 hours. The mean is approximately 19.98 hours.
- **Attendance**: The attendance percentage varies between 60% and 100%. The median attendance is 80%, with a mean of 79.98%.
- **Sleep Hours**: Students report sleeping between 4 and 10 hours per night, with a median of 7 hours and a mean of 7.03 hours.
- **Previous Scores**: Scores from previous assessments range from 50 to 100, with a median of 75 and a mean of 75.07.
- **Tutoring Sessions**: Students attended between 0 and 8 tutoring sessions. The median number of sessions is 1, while the mean is 1.49.
- **Physical Activity**: Physical activity engagement varies from 0 to 6 sessions, with a median of 3 sessions and a mean of 2.97.
- **Exam Score**: The exam scores range from 55 to 101, with a median score of 67 and a mean of 67.24.

## 3. Data types
<!-- 3. What data types do your data contain? -->
```{r}
sapply(data, class)
```

The data contains numeric and character data types.

## 4. New categorial variable
<!-- 4. Create a variable (new column) that categorizes the numeric variable as "High," "Medium," or
"Low". Use a conditional statement for this. -->
```{r}
# Add code here
```

## 5. Using a loop
<!-- 5. Use a loop to iterate through all rows and do the same task as in question 4, using conditions. -->
```{r}
# Add code here
```

## 6. Replace text
<!-- 6. Replace some text in one column with some other text -->
```{r}
# Add code here
```

## 7. Subset the data.frame
<!-- 7. Subset the data.frame with respect to one variable (categorical such as “region”, “gender” or “job-
sector”). (Hint: You will get an elegant way of solving it in week 40, but you do have tools to solve it
with the tools you’ve gotten so far) -->
```{r}
# Add code here
```

### 7.a. Number of instances
<!-- a. Count the number of instances (lines) from each category -->
```{r}
# Add code here
```

### 7.b. Mean
<!-- b. Calculate the mean of one on the numeric variables with respect to each category -->
```{r}
# Add code here
```

## 8. Reflection
<!-- 8. Use the results and your business knowledge to describe the situation. Including reflection on usage
of AI-tools. -->